Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-08-08 paper/agujournaltemplate.tex
Last version for submission

Finally, the data from some of the arrays are very noisy, which makes it hard to see a signal emerging when stacking over the one-minute-long time windows. We chose to keep only the locations for which the ratio between the maximum value of the stack of the envelopes of the cross-correlation functions to the root mean square is higher than 5. We compute the root mean square in cluster 1 for a time lag between 12 and 14s because we do not expect any reflected wave to arrive that late after a direct wave. The corresponding stack of the envelopes of the cross-correlation functions are shown in Figure 4 for the East-West component and the North-South component. The grey vertical line shows the theoretical time lag between the arrival of the direct P-wave and the arrival of the direct S-wave using the corresponding 1D velocity model for this array and the plate boundary model from ~\citeA{MCC_2006}, the dashed line corresponds to the slab model from ~\citeA{PRE_2003}. There is a good agreement between the timing of the peak and the theoretical time lag for most of the locations of the source of the tremor. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1cm},clip]{figures/BS_PWS_PWS_0.eps}
\caption{Stack of the envelopes of the cross-correlation signals for different positions of the tremor source relative to the Big Skidder array showing the cross-correlation between the East-West and the vertical components (red lines) and between the North-South and vertical components (blue lines). The theoretical S-minus-P times (grey dashed line for the Preston model) are generally in good agreement with the peaks in cross-correlation functions (grey solid line). The location of the tremor varies from west to east (left to right) and from south to north (bottom to top). The numbers next to each graph indicate the number of one-minute-long time windows in the best cluster. For clarity, we plotted only the part of the cross-correlation signal corresponding to timelags between 2 and 8 seconds.}
\label{pngfiguresample}
\end{figure}

>>>>

Finally, the data from some of the arrays are very noisy, which makes it hard to see a signal emerging when stacking over the one-minute-long time windows. We chose to keep only the locations for which the ratio between the maximum value of the stack of the envelopes of the cross-correlation functions to the root mean square is higher than 5. We compute the root mean square in cluster 1 for a time lag between 12 and 14 s because we do not expect any reflected wave to arrive that late after a direct wave. The corresponding stack of the envelopes of the cross-correlation functions are shown in Figure 4 for the East-West component and the North-South component. The grey dashed vertical line shows the theoretical time lag between the arrival of the direct P-wave and the arrival of the direct S-wave using the corresponding 1D velocity model for this array and the plate boundary model from ~\citeA{PRE_2003}, the grey solid line corresponds to the moment centroid of the stack. There is a good agreement between the timing of the centroid and the theoretical time lag for most of the locations of the source of the tremor. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1cm},clip]{figures/BS_PWS_PWS_0.eps}
\caption{Stack of the envelopes of the cross-correlation signals for different positions of the tremor source relative to the Big Skidder array showing the cross-correlation between the East-West and the vertical components (red lines) and between the North-South and vertical components (blue lines). The theoretical S-minus-P times (grey dashed line for the Preston model) are generally in good agreement with the centroids in cross-correlation functions (grey solid line). The location of the tremor varies from west to east (left to right) and from south to north (bottom to top). The numbers next to each graph indicate the number of one-minute-long time windows in the best cluster. For clarity, we plotted only the part of the cross-correlation signal corresponding to time lags between 2 and 8 seconds.}
\label{pngfiguresample}
\end{figure}

### 2021-08-08 paper/supplementary_material.tex
Last version for submission

\begin{center}
\includegraphics[width=\textwidth, trim={5cm 0.5cm 7.5cm 1.5cm},clip]{figures/BH_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Burnt Hill array.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 1.5cm},clip]{figures/CL_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Cat Lake array.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/DR_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Danz Ranch array.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 4cm},clip]{figures/GC_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Gold Creek array.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/LC_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Lost Cause array.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1.5cm 0.5cm 4.5cm 1.5cm},clip]{figures/PA_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Port Angeles array.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1.5cm},clip]{figures/TB_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Three Bumps array.}
\end{center}

>>>>

\begin{center}
\includegraphics[width=\textwidth, trim={5cm 0.5cm 7.5cm 1.5cm},clip]{figures/BH_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Burnt Hill array. See caption of Figure 4 for an explanation of this figure.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 1.5cm},clip]{figures/CL_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Cat Lake array. See caption of Figure 4 for an explanation of this figure.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/DR_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Danz Ranch array. See caption of Figure 4 for an explanation of this figure.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1.5cm 1cm 4.5cm 4cm},clip]{figures/GC_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Gold Creek array. See caption of Figure 4 for an explanation of this figure.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1cm 0.5cm 2.5cm 1.5cm},clip]{figures/LC_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Lost Cause array. See caption of Figure 4 for an explanation of this figure.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={1.5cm 0.5cm 4.5cm 1.5cm},clip]{figures/PA_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Port Angeles array. See caption of Figure 4 for an explanation of this figure.}
\end{center}

\begin{center}
\includegraphics[width=\textwidth, trim={2.5cm 0.5cm 5cm 1.5cm},clip]{figures/TB_PWS_PWS_0.eps}
\captionsetup{type=figure}
\captionof{figure}{Stacks of the envelopes of the cross correlation signals for different positions of the tremor source relative to the Three Bumps array. See caption of Figure 4 for an explanation of this figure.}
\end{center}
